---
title: "实证数据-地中海果蝇"
author: "SpencerWang"
date: "2024-08-03"
output: html_document
---
# function definition  
```{r}
setwd("C:/Users/Spenc/Desktop/manual_packages/FdaCluReg")
install.packages("C:/Users/Spenc/Desktop/manual_packages/FdaCluReg_0.0.0.18.tar.gz")
library(FdaCluReg)
ari_fun=function(x)
{
  library(igraph)
  ari_seq=NULL
  n=ncol(x)
  for (i in 2:n) 
  {
    for (j in 1:(i-1))
      {
      ari_seq=c(ari_seq,compare(x[,i],x[,j],method="adjusted.rand"))
    }
  }
  return(ari_seq)
}
library(fda)
```

# import the data  
```{r}
fly_dt=readLines("C:/users/spenc/desktop/simulation_results/new/real_dt/medfly1000.txt")
selected_fly_dt1=fly_dt[sapply(fly_dt,nchar)>50]
selected_fly_dt2=sapply(selected_fly_dt1,strsplit,split=" ")
#果蝇信息
cut_fun=function(x){return(x[[1]][1:7])}
fly_info_mat=matrix(unlist(lapply(selected_fly_dt2,cut_fun)),byrow = T,ncol = 7)
fly_info_mat=apply(fly_info_mat,2,as.numeric)
save(selected_fly_dt2,file = "C:/users/spenc/desktop/simulation_results/new/real_dt/fly_dt_list.RData")
save(fly_info_mat,file = "C:/users/spenc/desktop/simulation_results/new/real_dt/fly_info_mat.RData")
load("C:/users/spenc/desktop/simulation_results/new/real_dt/fly_dt_list.RData")
load("C:/users/spenc/desktop/simulation_results/new/real_dt/fly_info_mat.RData")

cut_fun=function(x){return(x[1:7])}
fly_info_mat=matrix(unlist(lapply(selected_fly_dt2,cut_fun)),byrow = T,ncol = 7)
#产卵记录
record_mat=matrix(rep(0,90*1000),nrow = 1000)
for (i in 1:1000) 
{
  temp_l=length(selected_fly_dt2[[i]])
  temp_record=as.numeric(selected_fly_dt2[[i]][-(1:7)])
  record_mat[i,1:min(90,temp_l-7)]=temp_record[1:min(90,temp_l-7)]
}
record_mat=apply(record_mat,2,as.numeric)
fly_info_df=data.frame(id=fly_info_mat[,1],eggs_all=fly_info_mat[,2],life=fly_info_mat[,7])
write.csv(record_mat,"C:/users/spenc/desktop/simulation_results/new/real_dt/fly_egg_record.csv")
write.csv(fly_info_df,"C:/users/spenc/desktop/simulation_results/new/real_dt/fly_info_df.csv")
1
```
# define clustering regression function in  this example  
```{r}
record_mat_ori=read.csv("C:/users/spenc/desktop/simulation_results/new/real_dt/fly_egg_record.csv")
fly_info_df=read.csv("C:/users/spenc/desktop/simulation_results/new/real_dt/fly_info_df.csv")
record_mat=apply(record_mat_ori[,-1],2,as.numeric)
#数据筛选-选取前30天的产卵记录还有剩余存活天数
demand_index=fly_info_df$life>30
fly_info_df_needed=fly_info_df[demand_index,]
record_mat_needed=t(record_mat[demand_index,1:30])#取对数
life_time_remain=as.numeric(fly_info_df_needed$life)-30

basis_need=create.bspline.basis(c(seq(1,30,3),30),norder = 4)
fd_test=smooth.basis(1:30,record_mat_needed,basis_need)



fly_clureg=function(seed,method="ls")
{
  library(FdaCluReg)
  library(fda)
  basis_need=create.bspline.basis(c(seq(1,30,3),30),norder = 4)
  temp_res_gibbs=gibbs_clusterwise_regression_auto(X_list = list(record_mat_needed),Y=life_time_remain,basis = basis_need,sample_t = 1:30,true_label = rep(1,length(life_time_remain)),K_max = 4,seed = seed,method = method,lambda = 1,rounds = 110)
  temp_res_2021=clusterwise_reg_2021_auto(X_list = list(record_mat_needed),Y=life_time_remain,basis = basis_need,sample_t = 1:30,true_label = rep(1,length(life_time_remain)),K_max = 4,seed = seed,method = method)
  save(temp_res_gibbs,file = paste("C:/users/spenc/desktop/simulation_results/new/real_dt/gibbs/logit",seed,".RData",sep = ""))
  save(temp_res_2021,file = paste("C:/users/spenc/desktop/simulation_results/new/real_dt/2021/logit",seed,".RData",sep = ""))
  return(seed)
}
```

carry out the experiment with 50 repetitions under different method setting. Experiment results should be stored first before moving on to another experiment otherwise the previous results will be covered.   

```{r}
num_cores=10
library(parallel)
cl=makeCluster(num_cores)
clusterExport(cl,  envir = environment(),varlist =c("record_mat_needed","life_time_remain"))
parLapply(cl,1:50,fly_clureg,method="ls")
```


# Summary and visualization for LAD methods
## fd coefficient of GCFLR-eBIC(LAD)  
```{r}
library(ggplot2)
LAD_ari=NULL
#here is the directory where the experiment results are stored 
file_list=paste("C:/users/spenc/desktop/simulation_results/new/real_dt/lad/gibbs/",dir("C:/users/spenc/desktop/simulation_results/new/real_dt/lad/gibbs"),sep="")

#样例结果用于画图
load(file_list[1])
#函数型系数的ggplot画图df
sample_t=seq(1,30,0.2)
temp_res=temp_res_gibbs
fd_df=eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[1]])

K_eBIC=NULL#类簇个数记录
label_record=NULL#最终标签记录ARI 计算
coef_record=c(0,0,0)#函数型系数基展开系数记录

for(i in 1:length(file_list))
{
load(file_list[i])
temp_res=temp_res_gibbs
K_eBIC=c(K_eBIC,temp_res$K_eBIC)
#类簇划分数量分布
number_sum=as.numeric(table(temp_res$selected_res_eBIC$labels))
#函数型系数的ggplot画图df添加新数据
fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[1]]))
for (j in 2:length(temp_res$selected_res_eBIC$beta_fd[[1]]))
{fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[j]]))}
#标签记录
label_record=c(label_record,temp_res$selected_res_eBIC$labels[[1]])
#系数可视化
coef_record=cbind(coef_record,temp_res$selected_res_eBIC$coefficients[[1]])
}
#数据
label_record=matrix(label_record,ncol = length(file_list))
ari_record=ari_fun(label_record)
coef_record=coef_record[,-1]
fd_df=fd_df[,-1]

LAD_ari=c(LAD_ari,ari_record)
#可视化
plot_fd=data.frame(time=rep(sample_t,ncol(fd_df)),value=as.vector(fd_df),group=rep(1:ncol(fd_df),each=length(sample_t)))
p=ggplot(plot_fd,aes(x=time,y=value,group=factor(group)))+geom_line(alpha=0.1,size=0.8)+
  geom_hline(yintercept = 0,linetype="dashed",color="red",size=0.5)+
  theme(panel.background = element_rect(fill = "white"),
        axis.line = element_line(colour="black"))+
  labs(title = "GCFLR-eBIC(LAD)")
# fd coefficient of GCFLR-eBIC(LAD)
p1=p
```
## fd coefficient of CFLR-eBIC(LAD)  
```{r}
file_list=paste("C:/users/spenc/desktop/simulation_results/new/real_dt/lad/2021/",dir("C:/users/spenc/desktop/simulation_results/new/real_dt/lad/2021"),sep="")
#样例结果用于画图
load(file_list[1])
#函数型系数的ggplot画图df
sample_t=seq(1,30,0.2)
temp_res=temp_res_2021
fd_df=eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[1]])

K_eBIC=NULL#类簇个数记录
label_record=NULL#最终标签记录ARI 计算
coef_record=c(0,0,0)#函数型系数基展开系数记录

for(i in 1:length(file_list))
{
load(file_list[i])
temp_res=temp_res_2021
K_eBIC=c(K_eBIC,temp_res$K_eBIC)
#类簇划分数量分布
number_sum=as.numeric(table(temp_res$selected_res_eBIC$labels))
#函数型系数的ggplot画图df添加新数据
fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[1]]))
for (j in 2:length(temp_res$selected_res_eBIC$beta_fd[[1]]))
{fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[j]]))}
#标签记录
label_record=c(label_record,temp_res$selected_res_eBIC$labels[[1]])
#系数可视化
coef_record=cbind(coef_record,temp_res$selected_res_eBIC$coefficients[[1]])
}

label_record=matrix(label_record,ncol = length(file_list))
ari_record=ari_fun(label_record)
coef_record=coef_record[,-1]
fd_df=fd_df[,-1]
LAD_ari=c(LAD_ari,ari_record)
#可视化
plot_fd=data.frame(time=rep(sample_t,ncol(fd_df)),value=as.vector(fd_df),group=rep(1:ncol(fd_df),each=length(sample_t)))
p=ggplot(plot_fd,aes(x=time,y=value,group=factor(group)))+geom_line(alpha=0.1,size=0.8)+
  geom_hline(yintercept = 0,linetype="dashed",color="red",size=0.5)+
  theme(panel.background = element_rect(fill = "white"),
        axis.line = element_line(colour="black"))+
  labs(title = "CFLR-eBIC(LAD)")
  
p2=p
```
## fd coefficient of CFLR-BIC(LAD)
```{r}

file_list=paste("C:/users/spenc/desktop/simulation_results/new/real_dt/lad/2021/",dir("C:/users/spenc/desktop/simulation_results/new/real_dt/lad/2021"),sep="")
#样例结果用于画图
load(file_list[1])
#函数型系数的ggplot画图df
sample_t=seq(1,30,0.2)
temp_res=temp_res_2021
fd_df=eval.fd(sample_t,temp_res$selected_res_BIC$beta_fd[[1]][[1]])

K_BIC=NULL#类簇个数记录
label_record=NULL#最终标签记录ARI 计算
coef_record=c(0,0,0)#函数型系数基展开系数记录

for(i in 1:length(file_list))
{
load(file_list[i])
temp_res=temp_res_2021
K_BIC=c(K_BIC,temp_res$K_BIC)
#类簇划分数量分布
number_sum=as.numeric(table(temp_res$selected_res_BIC$labels))
#函数型系数的ggplot画图df添加新数据
fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_BIC$beta_fd[[1]][[1]]))
for (j in 2:length(temp_res$selected_res_BIC$beta_fd[[1]]))
{fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_BIC$beta_fd[[1]][[j]]))}
#标签记录
label_record=c(label_record,temp_res$selected_res_BIC$labels[[1]])
#系数可视化
coef_record=cbind(coef_record,temp_res$selected_res_BIC$coefficients[[1]])
}

label_record=matrix(label_record,ncol = length(file_list))
ari_record=ari_fun(label_record)
coef_record=coef_record[,-1]
fd_df=fd_df[,-1]
LAD_ari=c(LAD_ari,ari_record)
#可视化
plot_fd=data.frame(time=rep(sample_t,ncol(fd_df)),value=as.vector(fd_df),group=rep(1:ncol(fd_df),each=length(sample_t)))
p=ggplot(plot_fd,aes(x=time,y=value,group=factor(group)))+geom_line(alpha=0.1,size=0.8)+
  geom_hline(yintercept = 0,linetype="dashed",color="red",size=0.5)+
  theme(panel.background = element_rect(fill = "white"),
        axis.line = element_line(colour="black"))+
  labs(title = "CFLR-BIC(LAD)")
  
p3=p

```
## ARI summary  
```{r}
LAD_ari_mat=matrix(LAD_ari,ncol = 3)
LAD_ari_plot=data.frame(CFLR_BIC=LAD_ari_mat[,3],CFLR_eBIC=LAD_ari_mat[,2],GCFLR_eBIC=LAD_ari_mat[,1])
colnames(LAD_ari_plot)=c("CFLR-BIC(LAD)","CFLR-eBIC(LAD)","GCFLR-eBIC(LAD)")
```

# Summary and visualization for LS methods  
## fd coefficient of GCFLR-eBIC(LS)  
```{r}
LS_ari=NULL
```


```{r}
file_list=paste("C:/users/spenc/desktop/simulation_results/new/real_dt/ls/gibbs/",dir("C:/users/spenc/desktop/simulation_results/new/real_dt/ls/gibbs"),sep="")

#样例结果用于画图
load(file_list[1])
#函数型系数的ggplot画图df
sample_t=seq(1,30,0.2)
temp_res=temp_res_gibbs
fd_df=eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[1]])

K_eBIC=NULL#类簇个数记录
label_record=NULL#最终标签记录ARI 计算
coef_record=c(0,0,0)#函数型系数基展开系数记录

for(i in 1:length(file_list))
{
load(file_list[i])
temp_res=temp_res_gibbs
K_eBIC=c(K_eBIC,temp_res$K_eBIC)
#类簇划分数量分布
number_sum=as.numeric(table(temp_res$selected_res_eBIC$labels))
#函数型系数的ggplot画图df添加新数据
fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[1]]))
for (j in 2:length(temp_res$selected_res_eBIC$beta_fd[[1]]))
{fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[j]]))}
#标签记录
label_record=c(label_record,temp_res$selected_res_eBIC$labels[[1]])
#系数可视化
coef_record=cbind(coef_record,temp_res$selected_res_eBIC$coefficients[[1]])
}

label_record=matrix(label_record,ncol = length(file_list))
ari_record=ari_fun(label_record)
coef_record=coef_record[,-1]
fd_df=fd_df[,-1]
LS_ari=c(LS_ari,ari_record)
#可视化

plot_fd=data.frame(time=rep(sample_t,ncol(fd_df)),value=as.vector(fd_df),group=rep(1:ncol(fd_df),each=length(sample_t)))
p=ggplot(plot_fd,aes(x=time,y=value,group=factor(group)))+geom_line(alpha=0.1,size=0.8)+
  geom_hline(yintercept = 0,linetype="dashed",color="red",size=0.5)+
  theme(panel.background = element_rect(fill = "white"),
        axis.line = element_line(colour="black"))+
  labs(title = "GCFLR-eBIC(LS)")
  
p4=p
```
## fd coefficient of CFLR-eBIC(LS)  
```{r}
file_list=paste("C:/users/spenc/desktop/simulation_results/new/real_dt/ls/2021/",dir("C:/users/spenc/desktop/simulation_results/new/real_dt/ls/2021"),sep="")
#样例结果用于画图
load(file_list[1])
#函数型系数的ggplot画图df
sample_t=seq(1,30,0.2)
temp_res=temp_res_2021
fd_df=eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[1]])

K_eBIC=NULL#类簇个数记录
label_record=NULL#最终标签记录ARI 计算
coef_record=c(0,0,0)#函数型系数基展开系数记录

for(i in 1:length(file_list))
{
load(file_list[i])
temp_res=temp_res_2021
K_eBIC=c(K_eBIC,temp_res$K_eBIC)
#类簇划分数量分布
number_sum=as.numeric(table(temp_res$selected_res_eBIC$labels))
#函数型系数的ggplot画图df添加新数据
fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[1]]))
for (j in 2:length(temp_res$selected_res_eBIC$beta_fd[[1]]))
{fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_eBIC$beta_fd[[1]][[j]]))}
#标签记录
label_record=c(label_record,temp_res$selected_res_eBIC$labels[[1]])
#系数可视化
coef_record=cbind(coef_record,temp_res$selected_res_eBIC$coefficients[[1]])
}

label_record=matrix(label_record,ncol = length(file_list))
ari_record=ari_fun(label_record)
coef_record=coef_record[,-1]
fd_df=fd_df[,-1]
LS_ari=c(LS_ari,ari_record)
#可视化

plot_fd=data.frame(time=rep(sample_t,ncol(fd_df)),value=as.vector(fd_df),group=rep(1:ncol(fd_df),each=length(sample_t)))
p=ggplot(plot_fd,aes(x=time,y=value,group=factor(group)))+geom_line(alpha=0.1,size=0.8)+
  geom_hline(yintercept = 0,linetype="dashed",color="red",size=0.5)+
  theme(panel.background = element_rect(fill = "white"),
        axis.line = element_line(colour="black"))+
  labs(title = "CFLR-eBIC(LS)")
  
p5=p
```
## fd coefficient of CFLR-BIC(LS)  
```{r}

file_list=paste("C:/users/spenc/desktop/simulation_results/new/real_dt/ls/2021/",dir("C:/users/spenc/desktop/simulation_results/new/real_dt/ls/2021"),sep="")
#样例结果用于画图
load(file_list[1])
#函数型系数的ggplot画图df
sample_t=seq(1,30,0.2)
temp_res=temp_res_2021
fd_df=eval.fd(sample_t,temp_res$selected_res_BIC$beta_fd[[1]][[1]])

K_BIC=NULL#类簇个数记录
label_record=NULL#最终标签记录ARI 计算
coef_record=c(0,0,0)#函数型系数基展开系数记录

for(i in 1:length(file_list))
{
load(file_list[i])
temp_res=temp_res_2021
K_BIC=c(K_BIC,temp_res$K_BIC)
#类簇划分数量分布
number_sum=as.numeric(table(temp_res$selected_res_BIC$labels))
#函数型系数的ggplot画图df添加新数据
fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_BIC$beta_fd[[1]][[1]]))
for (j in 2:length(temp_res$selected_res_BIC$beta_fd[[1]]))
{fd_df=cbind(fd_df,eval.fd(sample_t,temp_res$selected_res_BIC$beta_fd[[1]][[j]]))}
#标签记录
label_record=c(label_record,temp_res$selected_res_BIC$labels[[1]])
#系数可视化
coef_record=cbind(coef_record,temp_res$selected_res_BIC$coefficients[[1]])
}

label_record=matrix(label_record,ncol = length(file_list))
ari_record=ari_fun(label_record)
coef_record=coef_record[,-1]
fd_df=fd_df[,-1]
LS_ari=c(LS_ari,ari_record)
#可视化

plot_fd=data.frame(time=rep(sample_t,ncol(fd_df)),value=as.vector(fd_df),group=rep(1:ncol(fd_df),each=length(sample_t)))
p=ggplot(plot_fd,aes(x=time,y=value,group=factor(group)))+geom_line(alpha=0.1,size=0.8)+
  geom_hline(yintercept = 0,linetype="dashed",color="red",size=0.5)+
  theme(panel.background = element_rect(fill = "white"),
        axis.line = element_line(colour="black"))+
  labs(title = "CFLR-BIC(LS)")
  
p6=p

```
## ARI summary
```{r}
LS_ari_mat=matrix(LS_ari,ncol = 3)
LS_ari_plot=data.frame(CFLR_BIC=LS_ari_mat[,3],CFLR_eBIC=LS_ari_mat[,2],GCFLR_eBIC=LS_ari_mat[,1])
colnames(LS_ari_plot)=c("CFLR-BIC(LS)","CFLR-eBIC(LS)","GCFLR-eBIC(LS)")
```


# visualization of fd coefficients  
```{r}
library(patchwork)
p_list_lad=vector("list",3)
p_list_lad[[1]]=p3;p_list_lad[[2]]=p2;p_list_lad[[3]]=p1
p_lad=wrap_plots(p_list_lad, ncol = 3)


p_list_ls=vector("list",3)
p_list_ls[[1]]=p6;p_list_ls[[2]]=p5;p_list_ls[[3]]=p4
p_ls=wrap_plots(p_list_ls, ncol = 3)


```
```{r}
plot_parameter=c(14,12,0.5)
p1=p1+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))
p2=p2+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))
p3=p3+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))
p4=p4+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))
p5=p5+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))
p6=p6+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))
```

```{r}
p_list_all=vector("list",6)
p_list_all[[1]]=p6;p_list_all[[2]]=p5;p_list_all[[3]]=p4
p_list_all[[4]]=p3;p_list_all[[5]]=p2;p_list_all[[6]]=p1
p_all=wrap_plots(p_list_all, ncol = 3)
#输出大小 w1000 h750
p_all
```

# visualization of ari distributions  
```{r}
par(mfrow=c(1,2))
boxplot(LS_ari_plot)
boxplot(LAD_ari_plot)
plot_dt=data.frame(type=c(rep(colnames(LS_ari_plot),each=1225),rep(colnames(LAD_ari_plot),each=1225)),value=c(as.numeric(as.matrix(LS_ari_plot)),as.numeric(as.matrix(LAD_ari_plot))))
plot_dt$type=factor(plot_dt$type,levels = c(colnames(LS_ari_plot),colnames(LAD_ari_plot)))
p_boxplot=ggplot(data=plot_dt,mapping = aes(x=type,y=value))+
    geom_boxplot(fatten=1.5)+
  labs(x="",y="ARI")+
  theme(panel.background = element_rect(fill = "white", color = "black"),panel.grid.major  = element_line(color ="grey",linetype = "dotted"))+
    scale_y_continuous(limits = c(0, 1))+
     theme(axis.text.x=element_text(size=9,angle=0))
plot_parameter=c(14,13,0.5)
p_boxplot=p_boxplot+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))
#图像大小 w1000 h500
```


# data decriptive visualizations   
```{r}
record_mat_ori=read.csv("C:/users/spenc/desktop/simulation_results/new/real_dt/fly_egg_record.csv")
fly_info_df=read.csv("C:/users/spenc/desktop/simulation_results/new/real_dt/fly_info_df.csv")
record_mat=apply(record_mat_ori[,-1],2,as.numeric)
#数据筛选-选取前30天的产卵记录还有剩余存活天数
demand_index=fly_info_df$life>30
fly_info_df_needed=fly_info_df[demand_index,]
record_mat_needed=t(record_mat[demand_index,1:30])#取对数
life_time_remain=as.numeric(fly_info_df_needed$life)-30
demand_index=apply(record_mat_needed,2,sum)>0
basis_need=create.bspline.basis(c(seq(1,30,3),30),norder = 4)
fd_test=smooth.basis(1:30,record_mat_needed,basis_need)
fd_plot_mat=as.matrix(eval.fd(sample_t,fd_test$fd[demand_index,]))
fd_plot_df=data.frame(time=rep(sample_t,ncol(fd_plot_mat)),value=as.numeric(fd_plot_mat),
                      group=rep(1:ncol(fd_plot_mat),each=length(sample_t)))

#平滑结果
p_smoothed=ggplot(fd_plot_df,aes(x=time,y=value,group=factor(group)))+geom_line(alpha=0.1)+
  theme(panel.background = element_rect(fill = "white"),
        axis.line = element_line(colour="black"))


basis_need=create.bspline.basis(c(seq(1,30,3),30),norder = 4)
fd_test=smooth.basis(1:30,record_mat_needed,basis_need)
fd_pca=pca.fd(fd_test$fd,nharm = 2)


pca_score=data.frame(fd_pca$scores)
plot_pca_score_df=data.frame(score1=pca_score$X1,score2=pca_score$X2,value=life_time_remain)
#主成分得分图
p_pc_scores=ggplot(data=plot_pca_score_df,mapping = aes(x=score1,y=score2,color=value))+
  geom_point()+
  scale_color_gradient(low = "blue",high = "red")+  theme(panel.background = element_rect(fill = "white"),
        axis.line = element_line(colour="black"))+xlab("1st FPC scores")+ylab("2nd FPC scores")

#主成分图
fpc_mat=as.matrix(eval.fd(sample_t,fd_pca$harmonics))
fpc_mat[,2]=fpc_mat[,2]
fpc_df=data.frame(time=rep(sample_t,2),value=as.numeric(fpc_mat),group=rep(1:2,each=length(sample_t)))
p_fpc=ggplot(data=fpc_df,mapping = aes(x=time,y=value,color=factor(group)))+
  geom_line()+scale_color_manual(values = c("1"="red","2"="blue"))+
  theme(panel.background = element_rect(fill = "white"),
        axis.line = element_line(colour="black"))+
  theme(legend.position = "none")


#全部三个图
plot_fda=vector("list",3)
plot_parameter=c(14,12,0.5)
p_smoothed=p_smoothed+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))#+labs(caption = "(a)") + theme(plot.caption = element_text(hjust = 0.5, size = 12))#, face = "bold"
p_fpc=p_fpc+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))#+labs(caption = "(b)") + theme(plot.caption = element_text(hjust = 0.5, size = 12))
p_pc_scores=p_pc_scores+theme(axis.title.x =element_text(size = plot_parameter[1]),axis.title.y =element_text(size = plot_parameter[1]),
         axis.text.x = element_text(size = plot_parameter[2]),axis.text.y = element_text(size = plot_parameter[2]),
         axis.line = element_line(linewidth  = plot_parameter[3]))#+ labs(caption = "(c)") + theme(plot.caption = element_text(hjust = 0.5, size = 12))

plot_fda[[1]]=p_smoothed;plot_fda[[2]]=p_fpc;plot_fda[[3]]=p_pc_scores
library(patchwork)
p_fda=wrap_plots(plot_fda[1:3], ncol = 3)



p_fda
#画图参数 w1000 h450
p_smoothed
p_fpc
p_pc_scores
#小图 400 400
```

